The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-03-03 ms.tex
Convert references to bibtex
There were lots of entries in the reference list that were never
refered to in the text.  I have omitted most of those.

\section{INTRODUCTION}
\label{sec:introduction}
NGC 6210 is a bright and relatively large PN in the northern sky. The first photographic image of NGC 6210 was published by \citet{Duncan37}. In that old, fuzzy image a pair of twisted arms protruding in opposite directions from a blurred,  bright, nebular core are apparent. Several studies have discussed the inner kinematic motions of this object, e.g. \citet{Osterbrock66, Weedman68, Becker84, Icke89}. However, none of those studies had the spatial coverage and spectral resolution needed to produce a reliable spatio-kinematic model of this PN. 
The best kinematic study to date on NGC 6210 is probably the one published by \citet{Phillips96}  who obtained 11 long-slits centered on the nebular core, with each slit at different position angles thus providing a good spatial coverage but with only limited, low and medium spectral resolution. From these data  they suggested a  reasonable kinematic model for the ionized nebula. NGC 6210 jumped into fame thanks to the {\it HST} images obtained during the 1996 - 1998 period under the observing programs 6347 (K. Borkowski), 6792 (R. Rubin), 7501 (A. Hajian)  and 11122 (B. Balick). These images showed for the first time the extraordinarily complex morphology of NGC 6210. Incidentally the  {\it HST} and ground-based imagery prompted the nickname "the turttle" for this nebula, given the shape of its main body and extended arms that resemble the shell of a turttle with a long neck and its fins. The distance estimates to NGC 6210 vary roughly from 1.5 to 2.0 kpc. \citep{Hajian95} derive a distance to NGC 6210 from VLA 6 cm  expansion parallax measurements of 1.57$\pm0.40$ kpc, considering an expansion distance of 23 \kms

@@

Long-slit, echelle, spectroscopic observations of the nebula NGC~6210
were performed with the 2.1~m telescope at the Observatorio
Astron\'omico Nacional at San Pedro M\'artir, (OAN-SPM), Baja
California, M\'exico. We used the Manchester Echelle Spectrometer
(MES-SPM) \citep{Meaburn03} on the 2.1 m telescope in its $f$/7.5
configuration.  The MES-SPM is a long-slit, echelle spectrometer that
has no cross-disperser; it isolates single orders using interference
filters. For the 2003, 2004 and 2011 of the present observations, we used a
SITE-3 CCD detector with 1024 $\times$ 1024 square pixels, each 24
$\mu$m on a side ($\equiv$0.312 arcsec pixel$^{-1}$). The detector
was set to a binning of 2 $\times$ 2 in both the spatial and spectral
directions. Consequently, 512 increments, each 0\farcs624{} long gave
a projected slit length of 5\farcm32 on the sky. A TEK-1 CCD detector
was used for the 1998 data set with 1024$\times$1024 pixels$^2$ with
sides measuring 24 $\mu$m, using 2$\times$2 binning ($\equiv$0.62 arcsec
pixel$^{-1}$ and 3.5 \kms pixel$^{-1}$). For the 2001 and 2013 we used
a Marconi CCD detector with 2048 $\times$ 2048 square pixels, each 13.6
$\mu$m on a side. The detector was set to a binning of 2 $\times$ 2 in
both the spatial and spectra directions. Consequently, 1024
increments, each 0\farcs352{} long gave a projected slit length of
5\farcm47 on the sky.

@@

The log of spectroscopy observation is given in Table 1 divided into
dates, number of spectra, exposure times, spectral range, resolution,
slit wide, position angle and name of the slit (see Figure~1). 
The high resolution data are available in San Pedro M\'artir Kinematic Catalogue
of Galactic Planetary Nebulae (http://kincatpn.astrosen.unam.mx)
\citep{Lopez12}.

@@

\vfill \eject

%\bibliographystyle{astroads}
\begin{thebibliography}{}

\bibitem[L\'opez et al.(2012)]{Lopez12} L\'opez, J. A., Richer, M. G.,
  Garc\'ia-D\'iaz, M. T., Clark, D. M., Meaburn, J., Riesgo, H., Steffen,
  W., \& Lloyd, M. 2012, RevMexAA, 48, 3

\bibitem[Meaburn et al.(2003)]{Meaburn03} Meaburn, J., L\'opez,
J. A., Guti\'errez, L., Quir\'oz, F., Murillo, J. M. \& Vald\'ez, J.
2003, RMxAA, 39, 185M

\bibitem[Osterbrock et al.(1966)]{Osterbrock66} Osterbrock, D. E., Miller,
  J. S., \& Weedman, D. W. 1966, \apj, 145, 697

\bibitem[Weedman(1968)]{Weedman68} Weedman, D. W. 1968, \apj, 153, 49

\bibitem[Becker et al.(1984)]{Becker84} Becker, I., Gieseking, F. \& Solf, J.1984, 
Mitteilungen der Astronomishen Gesellschaft Hamburg, 62, 253

\bibitem[Icke et al.(2005)]{Icke89} Icke, V., Preston, H. \& Balick, B.
 1989, \aj, 97, 4621

\bibitem[Balick et al.(1998)]{Balick98} Balick B., Alexander J.,
  Hajian A. R., Terzian Y., Perinotto M., \& Patriarchi P. 1998,
  \apj, 116, 360

\bibitem[Balick et al.(1987a)]{Balick87a} Balick, B., Preston, H. L.,
  Icke, V. 1987a, \aj, 94, 1641B

\bibitem[Balick(1987c)]{Balick87c} Balick B. 1987c, \aj, 94, 671

\bibitem[Ciardullo et al.(1999)]{Ciardullo99} Ciardullo, R., Bond,
  H. E., Sipior, M. S., Fullton, L. K., Zhang, C.-Y., Schaefer,
  K. G. 1999, \aj, 118, 488

 \bibitem[Clark et al.(2010)]{clark10} Clark, D.~M., 
Garc{\'{\i}}a-D{\'{\i}}az, M.~T., L{\'o}pez, J.~A., Steffen, W.~G., 
\& Richer, M.~G.\ 2010, \apj, 722, 1260

\bibitem[Duncan (1937)]{Duncan37} Duncan, J. C.. 1937, \apj 86, 496

\bibitem[Frew(2008)]{Frew08} Frew, D. J. 2008, Ph.D. Thesis, Department of Physics,
  Macquire University, NSW, 2109, Australia

 \bibitem[Garc{\'{\i}}a-D{\'{\i}}az et al.(2009)]{gd09} 
Garc{\'{\i}}a-D{\'{\i}}az, M.~T., Clark, D.~M., L{\'o}pez, J.~A., Steffen, 
W., \& Richer, M.~G.\ 2009, \apj, 699, 1633

\bibitem[Garc\'ia-D\'iaz \& Henney(2007)]{Garcia07} Garc\'ia-D\'iaz,
  Ma. T., \& Henney, W. J. 2007, \aj, 133, 952G

\bibitem[Gieseking et al.(1985)]{Gieseking85} Gieseking, F., Becker,
  I., \& Solf, J. 1985, \apj, 295L, 17G

\bibitem[Phillips \& Cuesta(1996)]{Phillips96} Phillips, J. P. \& Cuesta, L. 1996
, \aj, 111, 1227

\bibitem[Hajian \& Terzian(1995)]{Hajian95} Hajian, Y. \&  Terzian, Y., 1995, \aj 109 2600

\bibitem[Heap(1977)]{Heap77} Heap, S. R. 1977, \apj, 215, 864

\bibitem[Kastner et al.(2012)]{Kastner12} Kastner et al. 2012, arXiv:1204.6055

\bibitem[Kudritzki et al.(1997)]{Kudritzki97} Kudritzki, R. P., Mendez,
  R. H., Puls, J., McCarthy, J. K. 1997, IAUS, 180, 64

\bibitem[L\'opez et al.(2012a)]{lophb5} L\'opez, J. A., Garc\'{\i}a-D\'{\i}az, M. T., Steffen, W., Riesgo, H. \& Richer, M. G. 2012a, \apj, 750, 131

\bibitem[M\'endez et al.(2011)]{Mendez11} M\'endez, R. H., Urbaneja,
  M.A., Kudritzki, R. P. \& Prinja, R. K. 2011, IAUS 283, submitted.

\bibitem[O'Dell et al.(2002)]{Odell02} O'Dell, C. R., Balick, B., Hajian, A. R., Henney, W. J.
  \& Burkert, A. 2002, \aj 123, 3329

\bibitem[O'Dell \& Ball(1985)]{Odell85} O'Dell, C. R., \& Ball,
  M. E. 1985, \apj, 289, 526

\bibitem[Pauldrach et al.(2004)]{Pauldrach04} Pauldrach, A. W. A.,
  Hoffmann, T. L., \& Mendez, R. H. 2004, \aap, 419, 1111

\bibitem[Phillips \& Cuesta(1999)]{Phillips99} Phillips, J. P., \&
  Cuesta, L. 1999, \aj, 118, 2929

\bibitem[Pottasch et al.(2008)]{Pottasch08} Pottasch, S. R., Bernard-Salas, J.,
  \& Roelling T. L.  2008, \aap, 481, 393

\bibitem[Reed et al.(1999)]{Reed99} Reed, D. S., Balick, B., Hajian, A. R.,
  Klayton, T. L., Giovanardi, S., Casertano, S., Panagia, N., \&Terzian, Y.
  1999, \aj, 118, 2430

\bibitem[Stanghellini \& Shaw(2008)]{Stanghellini08}
  Stanghellini, L. \& Shaw, R. A. 2008, \apj, 689, 194

 \bibitem[Steffen et~al.(2010)]{shapeWo10} Steffen, W., Koning, N., Wenger, S., Morisset, C., \& Magnor, M.
 2010, IEEE, Transactions on Visualization and Computer Graphics, 17, No. 4, 454

\bibitem[Steffen \& L{\'o}pez(2006)]{shapeWo06} Steffen, W. \& L{\'o}pez, J.~A.
  2006, RMxAA, 42, 99

\bibitem[Tinkler \& Lamers(2002)]{Tinkler02} Tinkler, C. M., Lamers,
  H. J. G. L. M. 2002, \aap, 384, 987

\bibitem[Zhang et al.(2012)]{Zhang12} Zhang, Y., Fang, X., Chau, W., Hsia, C.-H., Liu, X.-W., Kwon, S., \& Koning, N. 2012, arXiv:1205.3470

\end{thebibliography}

@@

>>>>

\section{INTRODUCTION}
\label{sec:introduction}
NGC 6210 is a bright and relatively large PN in the northern sky. The first photographic image of NGC 6210 was published by \citet{Duncan:1937a}. In that old, fuzzy image a pair of twisted arms protruding in opposite directions from a blurred,  bright, nebular core are apparent. Several studies have discussed the inner kinematic motions of this object, e.g. \citet{Osterbrock:1966a, Weedman:1968a, Becker:1984a, Icke:1989a}. However, none of those studies had the spatial coverage and spectral resolution needed to produce a reliable spatio-kinematic model of this PN. 
The best kinematic study to date on NGC 6210 is probably the one published by \citet{Phillips:1996a}  who obtained 11 long-slits centered on the nebular core, with each slit at different position angles thus providing a good spatial coverage but with only limited, low and medium spectral resolution. From these data  they suggested a  reasonable kinematic model for the ionized nebula. NGC 6210 jumped into fame thanks to the {\it HST} images obtained during the 1996 - 1998 period under the observing programs 6347 (K. Borkowski), 6792 (R. Rubin), 7501 (A. Hajian)  and 11122 (B. Balick). These images showed for the first time the extraordinarily complex morphology of NGC 6210. Incidentally the  {\it HST} and ground-based imagery prompted the nickname "the turttle" for this nebula, given the shape of its main body and extended arms that resemble the shell of a turttle with a long neck and its fins. The distance estimates to NGC 6210 vary roughly from 1.5 to 2.0 kpc. \citep{Hajian:1995a} derive a distance to NGC 6210 from VLA 6 cm  expansion parallax measurements of 1.57$\pm0.40$ kpc, considering an expansion distance of 23 \kms

@@

Long-slit, echelle, spectroscopic observations of the nebula NGC~6210
were performed with the 2.1~m telescope at the Observatorio
Astron\'omico Nacional at San Pedro M\'artir, (OAN-SPM), Baja
California, M\'exico. We used the Manchester Echelle Spectrometer
(MES-SPM) \citep{Meaburn:2003a} on the 2.1 m telescope in its $f$/7.5
configuration.  The MES-SPM is a long-slit, echelle spectrometer that
has no cross-disperser; it isolates single orders using interference
filters. For the 2003, 2004 and 2011 of the present observations, we used a
SITE-3 CCD detector with 1024 $\times$ 1024 square pixels, each 24
$\mu$m on a side ($\equiv$0.312 arcsec pixel$^{-1}$). The detector
was set to a binning of 2 $\times$ 2 in both the spatial and spectral
directions. Consequently, 512 increments, each 0\farcs624{} long gave
a projected slit length of 5\farcm32 on the sky. A TEK-1 CCD detector
was used for the 1998 data set with 1024$\times$1024 pixels$^2$ with
sides measuring 24 $\mu$m, using 2$\times$2 binning ($\equiv$0.62 arcsec
pixel$^{-1}$ and 3.5 \kms pixel$^{-1}$). For the 2001 and 2013 we used
a Marconi CCD detector with 2048 $\times$ 2048 square pixels, each 13.6
$\mu$m on a side. The detector was set to a binning of 2 $\times$ 2 in
both the spatial and spectra directions. Consequently, 1024
increments, each 0\farcs352{} long gave a projected slit length of
5\farcm47 on the sky.

@@

The log of spectroscopy observation is given in Table 1 divided into
dates, number of spectra, exposure times, spectral range, resolution,
slit wide, position angle and name of the slit (see Figure~1). 
The high resolution data are available in San Pedro M\'artir Kinematic Catalogue
of Galactic Planetary Nebulae (http://kincatpn.astrosen.unam.mx)
\citep{Lopez:2012a}.

@@

@@

\bibliography{turtle-paper-refs}
